\documentclass{ctexart}
\title{Pre-project Homework for 3D Group Members}
\begin{document}
	\maketitle
	\section{Introduction}
	For any game developers, at least indie ones or small teams like us, choosing the right 3D game engine is the very first yet crucial step. With a dazzling variety of game engines being presented, three of them have been predetermined to reduce the workload of your investigation. They are Unity 5, Unreal Engine 4 and CryENGINE 3. Please answer the following questions with the joint intelligence of you all, with either English or Chinese. Do note that your provided answers will to some extent determine the final development environment where you will find pleasure working.
	\section{Questions}
	The following questions are mostly concerned with the comparison of the above-mentioned game engines. You may consider using examples, illustrating and referencing when giving answers. Remember to provide links to the sources if possible, as others may need to check them.
	\begin{enumerate}
		\item Supported programming languages
		\paragraph{Answer:}
		answer here:
		I also don't know what it is!
		\item Multi-platform deployment
		\item Hardware requirements for developers and users
		\item Community support and marketplace popularity
		\item Official help docs availability
		\item Game genres (e.g. RTS, FPS) favoritism
		\item Built-in modeling and animating system capability
		\item Graphics quality
		\item Work flow fluency
		\item Learning difficulty for indie developers and teams
	\end{enumerate}
	\textit{Hints: searching for the answers to any of the individual questions may not be a good starting point, as you're perhaps not even familiar with the questions at first! Search for general information about each game engines or comparisons, then see whether you can gain some further insights.}
	\section{Conclusion}
	After the investigation, we prefer to use \verb|\* decision *\| as our development environment.
	\newpage\appendix
	\section{Recommended Sources}
	\begin{enumerate}
		\item Official sites
		\item 3rd party critics
		\item Individuals' comments
	\end{enumerate}
\end{document}
liyanghao 611
